Properties of coronal Fourier power spectra and their implications for coronal seismology and coronal heating.

### 2014-04-28 tex/paper1/paper1.tex
editing paper: note - don't need the 68% and 95% confidence intervals in the plots of the geometric mean power spectra, as this is expressed in the distributions plots.  replace these plots with those showing the model fits to the data.
more edits to the paper

\section{Analysis}\label{sec:anal}

We wish to analyze the frequency content of these resulting datacubes
as a function of spatial location.  Four locations were chosen in the
data representing four different types of physical locations in the
solar atmosphere.  These were a quiet Sun region, a region that lies
on top of a sunspot, a footpoint region, and a coronal moss region.
Figures \ref{fig:loc171193} show the location of the regions on sample
images from the time range considered.

@@

The moss results for 171\AA\ and 193\AA\ are notably different from
the other results.  In comparison to the general trend observed in
other regions, there appears to be excess Fourier power in the range
1-10 mHz.  Previous studies (???) have shown that the moss is a source
of uncorrelated and incoherent Fourier power.  This suggests that a
second model for these regions should be considered.  The spectrum
$P_{1}$ where
\begin{equation}
\label{eq:pwrlawbunp}
P_{1}(f) = P_{0} + \alpha\exp\left[-\frac{(\ln(f)-\beta)^{2}}{2\sigma^{2}}\right]
\end{equation}
contains the previous power law dependence, plus a second term which
models any power over and above the power law.

\subsection{Comparing power spectra models}\label{ssec:twomodels}

@@

All the automated detection algorithms described above attempt to find
individual pixels that are obviously oscillating at some frequency,
using the strength of the oscillation at that frequency (compared to
some assumption of the background) as the key quantity to measure.
These pixels are then clumped together and the quality of the signal
is then assessed.  Detection algorithms based on wave coherence, such
as \cite{2008SoPh..252..321M}, implement wave detection through
finding spatially contiguous regions of the corona which are coherent
in a given frequency range.  The frequency range searched is based on
previous experience.  Oscillations that are detected propagating along
loops are often found by considering distance-time plots
\cite{demoortel2000} and looking for alternating brightening/darkening
in those plots as a indicator of a propagating wave.  This is
essentially a coherence-based approach, as the user is assessing the
likelihood that an oscillation has been detected based on the observed
signal in multiple contiguous pixels.  However, each pixel in these
plots probably has a red-noise background power spectrum, and so the
discussion of Section \ref{ssec:corseis} suggests that the
significance of any claimed oscillation is much reduced.  The effect
of a red-noise background signal on these coherence-based approaches
is not known.

>>>>

\section{Analysis}\label{sec:anal}
We wish to analyze the frequency content of these resulting datacubes
as a function of spatial location.  Four locations were chosen in the
data representing four different types of physical locations in the
solar atmosphere.  These were a quiet Sun region, a region that lies
on top of a sunspot, a footpoint region, and a coronal moss region.
Figures \ref{fig:loc171193} show the location of the regions on sample
images from the time range considered.

@@

The moss results for 171\AA\ and 193\AA\ are notably different from
the other results.  In comparison to the general trend observed in
other regions, there appears to be excess Fourier power in the range
1-10 mHz.  Previous studies (???) have shown that the moss is a source
of uncorrelated and incoherent Fourier power.  This suggests that a
second model for these regions should be considered.  The spectrum
$P_{1}$ where
\begin{equation}
\label{eq:pwrlawbump}
P_{1}(f) = P_{0} + \alpha\exp\left[-\frac{(\ln(f)-\beta)^{2}}{2\sigma^{2}}\right]
\end{equation}
contains the previous power law dependence, plus a second term which
models any power over and above the power law.

These two models are fit to the data (black solid lines, Figures
\ref{} and \ref{}). The

@@

All the automated detection algorithms described above attempt to find
individual pixels that are obviously oscillating at some frequency,
using the strength of the oscillation at that frequency (compared to
some assumption of the background) as the key quantity to measure.
These pixels are then clumped together and the quality of the signal
is then assessed.  Detection algorithms based on wave coherence, such
as \cite{2008SoPh..252..321M}, implement wave detection through
finding spatially contiguous regions of the corona which are coherent
in a given frequency range.  The frequency range searched is based on
previous experience.  Oscillations that are detected propagating along
loops are often found by considering distance-time plots
\cite{demoortel2000} and looking for alternating brightening/darkening
in those plots as a indicator of a propagating wave.  This is
essentially a coherence-based approach, as the user is assessing the
likelihood that an oscillation has been detected based on the observed
signal in multiple contiguous pixels.  However, each pixel in these
plots probably has a red-noise background power spectrum, and so the
discussion of Section \ref{ssec:corseis} suggests that the
significance of any claimed oscillation is much reduced.

\subsection{``Excess'' emission}\label{ssec:excess}
The models fits of Section \ref{sec:anal} indicate that equation
\ref{eq:pwrlaw} is preferred over equation \ref{eqn:pwrlawbump} as the
superior description of the observed Fourier power spectrum.  This
model is consistent with previous observations by TRACE of power in
the frequency range of 1 - 10 mHz.  The moss region shows the largest
presence of this excess emission.

It would be tempting to take this excess contribution and infer a
distribution of field line angles with the solar surface.  This
distribution relies on the assumption that all the
Gaussian-distributed component is entirely due to the channeling of
photospheric oscillatory power up to ``coronal'' heights and
temperatures.  However ??? has shown that moss has a relatively

The AIA 171\AA\ and 193\AA\ wavebands are relatively wide, and include
contributions from plasma at many different temperatures, heights in
the atmosphere, and many different elements \ref{}.  A deeper
understanding of the contributions from these different plasmas is
required before a good estimate of the distribution of the angle
coronal loop footpoints make with the surface can be made.

Finally, only two models of the Fourier power spectrum are considered.
The choice of equation \ref{eqn:pwrlawbump} is motivated by previous
observations.  However, other models are certainly possible.  For
example, \cite{1993ASPC...42..111H} modelled the
